---
title: "c_asthma_eda"
author: Sarah McLarnan
date: 09.29.2020
output: html_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

```

```{r gender}
data = readRDS("./data/misbath_05072020.rds") 


select_data = data %>%
  select(C_ASTHMA, newgendr)%>%
  mutate(gendr = as.factor(newgendr))


t.gendr = table(select_data$C_ASTHMA, select_data$gendr)
t.gendr = t.gendr[-3,]
t.gendr

chisq.test(t.gendr)

ggplot (select_data, aes(x=C_ASTHMA, fill = gendr)) +
  geom_bar(position = "dodge")

###unknown which genders 1 and 2 correspond to 

```

```{r covariates}
prenatal_sub = 
  data %>% 
  select(SID, C_ASTHMA, A18_0, B04_0, E10_0, E01_0, A11_0, A12_0, A13_0, A14_0, A15_0, A04_0) %>%
  mutate(
    race = as.factor(A18_0),
    asthma_pregdx = as.factor(B04_0), 
    smkr_house = as.factor(E10_0),
    smkr_cur = as.factor(E01_0),
    aff_food = as.factor(A11_0),
    aff_stay = as.factor(A12_0),
    aff_gaselec = as.factor(A13_0),
    aff_cloth = as.factor(A14_0),
    aff_med = as.factor(A15_0),
    high_deg = as.factor(A04_0))

prenatal_sub = 
 prenatal_sub %>%
 mutate(
  race = fct_recode(prenatal_sub$race, dominican = "3", hispanic = "4", africanamerican = "5"),
  asthma_pregdx = fct_recode(prenatal_sub$asthma_pregdx, yes = "1", no = "2"), 
  smkr_house = fct_recode(prenatal_sub$smkr_house,yes = "1", no = "2", dk = "8", nr  = "9"), 
  smkr_cur = fct_recode(prenatal_sub$smkr_cur,yes = "1", no = "2", dk = "8", nr  = "9"), 
  aff_food = fct_recode(prenatal_sub$aff_food, yes = "1", no = "2", dk = "8", nr  = "9"), 
  aff_stay = fct_recode(prenatal_sub$aff_stay, yes = "1", no = "2", dk = "8", nr  = "9"),
  aff_gaselec = fct_recode(prenatal_sub$aff_gaselec, yes = "1", no = "2", dk = "8", nr  = "9"),
  aff_cloth = fct_recode(prenatal_sub$aff_cloth, yes = "1", no = "2", dk = "8", nr  = "9"),
  aff_med = fct_recode(prenatal_sub$aff_med, yes = "1", no = "2", dk = "8", nr  = "9"),
  high_deg = fct_recode(prenatal_sub$high_deg, lesshigh = "1", somehigh = "2", high = "3", ged = "4", somecol = "5", col2yr = "6", col4yr = "7", grad = "8")) %>%
  select(SID, C_ASTHMA, race, asthma_pregdx, smkr_house, smkr_cur, aff_food, aff_stay, aff_gaselec, aff_cloth, aff_med, high_deg)
    
  
prenatal_sub = 
  subset(prenatal_sub, (C_ASTHMA == "Yes" | C_ASTHMA == "No"))
  
  
t.race = table(prenatal_sub$C_ASTHMA, prenatal_sub$race)
t.race = t.race[-3,-2]
t.race 

chisq.test(t.race)

t.asthma_pregdx = table(prenatal_sub$C_ASTHMA, prenatal_sub$asthma_pregdx)
t.asthma_pregdx = t.asthma_pregdx[-3,]
t.asthma_pregdx

chisq.test(t.asthma_pregdx)
  
  
t.smkr_house = table(prenatal_sub$C_ASTHMA, prenatal_sub$smkr_house)
t.smkr_house = t.smkr_house[-3,]
t.smkr_house

chisq.test(t.smkr_house)

  
t.smkr_cur = table(prenatal_sub$C_ASTHMA, prenatal_sub$smkr_cur)
t.smkr_cur = t.smkr_cur[-3,]
t.smkr_cur

chisq.test(t.smkr_cur)

t.aff_food = table(prenatal_sub$C_ASTHMA, prenatal_sub$aff_food)
t.aff_food = t.aff_food[-3,]
t.aff_food

chisq.test(t.aff_food)


t.aff_stay = table(prenatal_sub$C_ASTHMA, prenatal_sub$aff_stay)
t.aff_stay = t.aff_stay[-3,]
t.aff_stay
chisq.test(t.aff_stay)


t.aff_gaselec = table(prenatal_sub$C_ASTHMA, prenatal_sub$aff_gaselec)
t.aff_gaselec = t.aff_gaselec [-3,]
t.aff_gaselec

chisq.test(t.aff_gaselec)
  

t.aff_cloth = table(prenatal_sub$C_ASTHMA, prenatal_sub$aff_cloth)
t.aff_cloth = t.aff_cloth [-3,]
t.aff_cloth

chisq.test(t.aff_cloth)

  
t.aff_med = table(prenatal_sub$C_ASTHMA, prenatal_sub$aff_med)
t.aff_med = t.aff_med [-3,]
t.aff_med

chisq.test(t.aff_med)
  
  
t.high_deg = table(prenatal_sub$high_deg,prenatal_sub$C_ASTHMA)
t.high_deg = t.high_deg [-8,-3]
t.high_deg

chisq.test(t.high_deg)
```

### the only covariate statistically associated with C_ASTHMA is smoker in house

```{r SES covariates and PM2.5}
load("~/RESEARCH/Herbstman/ccceh_pm_dlm/data/pm_data.RDATA")

sub_m.data = full_join(prenatal_sub, ave.pm25.no2, by = "SID")

pm_race.aov = aov(ave.pm25.preg ~ race, data = sub_m.data)
summary(pm_race.aov)

pm_pregdx.aov = aov(ave.pm25.preg ~ asthma_pregdx, data = sub_m.data)
summary(pm_pregdx.aov)

pm_smkr_house.aov = aov(ave.pm25.preg ~ smkr_house, data = sub_m.data)
summary(pm_smkr_house.aov)

pm_smkr_cur.aov = aov(ave.pm25.preg ~ smkr_cur, data = sub_m.data)
summary(pm_smkr_cur.aov)

pm_aff_food.aov = aov(ave.pm25.preg ~ aff_food, data = sub_m.data)
summary(pm_aff_food.aov)

pm_aff_stay.aov = aov(ave.pm25.preg ~ aff_stay, data = sub_m.data)
summary(pm_aff_stay.aov)

pm_aff_gaselec.aov = aov(ave.pm25.preg ~ aff_gaselec, data = sub_m.data)
summary(pm_aff_gaselec.aov)

pm_aff_cloth.aov = aov(ave.pm25.preg ~ aff_cloth, data = sub_m.data)
summary(pm_aff_cloth.aov)

pm_aff_med.aov = aov(ave.pm25.preg ~ aff_med, data = sub_m.data)
summary(pm_aff_med.aov)

pm_high_deg.aov = aov(ave.pm25.preg ~ high_deg, data = sub_m.data)
summary(pm_high_deg.aov)

```
### the only covariates signficantly associated with average pregnancy PM2.5 are race and highest degree of education 
